---
title: "Título del informe"
#subtitle: "Subtítulo del informe"
author: |
  | Dirección Nacional de Mercados y Estadística
  | **SUBSECRETARÍA DE DESARROLLO ESTRATÉGICO**
date: "acalafecha"
output:
  comunicacion::template_informe
knit: pagedown::chrome_print
toc-title: "Índice"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```







# Algunos comandos para trabajar el formato de salida: {-}

```{r}
############# Algunos comandos para trabajar:

# *\newline*

# *\newpage*

# *\pagebreak*

```

## Second level {-}

This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.

This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.

This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.


+ item 1
+ item 2
+ item 3

1. numbered 1
2. numbered 2
3. numbered 3

## Second level {-}

Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

Finally, be sure to remove this message! This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.

This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.

This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

Finally, be sure to remove this message!This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

## Second level {-}

Finally, be sure to remove this message!
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.

This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

# And now part 2 {-}

This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.

## Second level {-}

This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

Finally, be sure to remove this message!

Finally, be sure to remove this message!This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

Finally, be sure to remove this message!This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

Finally, be sure to remove this message!This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
